The Astropy Project:

### 2017-10-04 main.tex
Update on Overleaf.
Add text for APEs

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
  SAO,][]{ds9}. These packages tend to address a wide range of users
and they typically provide some level of documentation and user
support. Other packages are developed foremost by individual research
groups and used mostly in work by members of this group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e. the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

>>>>

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate. I picked ds9 becase (a) it's wider known (e.g. in the X-ray sounity) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package. TOPCAT would have been another example if we want to expand that list.
  SAO,][]{ds9}. These packages tend to address a wide range of users
and they typically provide some level of documentation and user
support. Other packages are developed foremost by individual research
groups and used mostly in work by members of this group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e. the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
Central to the success of \astropy\ is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on an publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by a maintainer responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy\ has a mechanism to more formally propose
changes to the code management (e.g.\ the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community concensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy\ coordination comitee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python\ programming language.
